---
title: "Legislative Data"
author: "Hana"
date: "4/28/2018"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(dplyr)
library(httr)
library(jsonlite)
topic <- "taxation"
representative_id <- "S000510"
source("assignment.R")
```


```{r Representative Info, echo = FALSE}

name <- paste(member$first_name, member$last_name)
phone <- rep_roles_df[rep_roles_df$congress == "115", "phone"]
dotgov <- member$url  
twitter <- member$twitter_account

```
## Introduction
> This report, generated using information provided by ProPublica, is about the legislative branch of the U.S. government and has three major parts. Part one is a table of recent `r topic` related bills. Part two gives information on the `r bill_name`. Part three gives information about my local representative, `r name`. 

>The Legislative Branch, also called Congress, is made up of a group of people called legislators. The US has a bicameral legislature (meaning two houses of Congress). The two houses are the Senate, whose members are called senators, and the House of Representatives, whose members are called representatives or congressmen. Senators are elected for a six year term while representatives are elected for two year terms. 

>The Senate and the House introduce and amend their own versions of a bill they want to pass, but the Senate and the House must vote on and pass the exact same version of a bill.
>
> For a fun video on how a bill becomes a law, watch School House Rock's [I'm Just a Bill](https://www.youtube.com/watch?v=FFroMQlKiag). 




## Part One: Table of Tax Related Bills
```{r subject_table, echo = FALSE}

kable(bills_select_df) 

```

### Explanations and Summary
- **bill_id:** The first letters indicate what type of bill it is. "s" means Senate. "hr" means House of Representatives. "hconres" means house concurrent resolution. Concurrent resolutions are legislative measures adopted by both the Senate and the House of Representatives, and they are usually for internal governance. The number after is the bill's number. The number that appears after the dash is "115," which tells us that these bills come from the 115th Congress, the Congress that is in session between 2017 and 2018.
- **short_title:** Many of the bill titles are longer, but the short titles are probably what you hear in the news. For example, the long title of the `r bill_name` is "`r bill_long_title`". 
- **sponsor:** The format of the sponsor column is as follows: The sponsor, the sponsor's state (abbreviated), the sponsor's party (They are usually either Democrat or Republican), number of cosponsors.
- **latest_major_action:** If a bill introduced in the house and passes, the latest major action should read "Received in the Senate". It should be the other way around if it was introduced and passed in the Senate. If a bill is passed by both houses, then the latest major action should read "Presented to President." If a bill becomes a law, the latest major action should read "Became Public Law No: 115-xxx" with 115 meaning the 115th Congress.
- **congressdotgov_url:** Clicking on this url leads you to the congress.gov page for the bill.

## Part Two: Specific Bill

###`r bill_name`

#### Bill Basics
>`r bill_name` was sponsored by `r bill_sponsor` (`r sponsor_party`, `r sponsor_state`) and has `r cosponsors` cosponsors. Where the bill is now: `r latest_major_action`.

>Link to full [bill text](`r link_to_text`)

#### What Is It?
>The `r bill_name` reauthorizes funding for the FAA for the next five years. In response to recent incidents of involuntary bumping, the bill prohibits airliners from involuntarily bumping passengers once passengers are seated and directs the Secretary of Transportation to clarify compensation rules for involuntary bumping. The bill addresses some recent trends:

- There's been a recent uptick of pets on planes, which may explain why the bill addresses concerns about the rights of passengers with disibilities by calling for a review of best practices. 
- Vaping is becoming more popular. The bill amends the existing non-smoking law to apply to e-cigarettes. 
- If you feel like your seat has been getting smaller, this bill addresses that. The bill issues regulations establishing minimum seat dimension standards on passenger aircraft.

##### Other Bill Highlights

- Urges the FAA to investigate the recent Southwest Airlines airplane crash
- Provides for training FAA personnel on the latest technology 
- Requires the FAA to review advanced cockpit displays and evacuation procedures
- Addresses speeding up the regulation of drones. 
- Prohibits cellphone use and voice communications while in-flight
- Establishes of a Lithium Ion Battery Safety Advisory Committee
- Directs the FAA to esablish R&D programs to solve problems like air traffic surveillance over ocean (which, can't be done right now)

#### Should `r bill_name` Become Law?
> The `r bill_name` should become law. It has bipartisan support, provides funding for critical infrastructure, and addresses recent problems in the airline industry such as passenger bumping, increase in pets being brought on-board, and loss of planes in the middle of the ocean (think Malaysia Airlines Flight 370).


#### Bill Actions
>On `r passed_house`, the `r bill_name` passed the House with a vote of `r yes_faa`-`r no_faa`. It was voted on `r num_times_faa_voted_on` times, including amendments and passage. It will now go to the Senate to be voted on.

## Part 3: Representative

### `r name`
- Phone Number: `r phone`
- Twitter Account: `r twitter`
- Website: `r dotgov`

#### Table of Recent Bills Sponsored

`r kable(sponsored_and_cosponsored)`

`r name` voted against his party `r pct_rep_vote_with_other_party`% of the time in the 115th Congress.

##Sources:
- [Concurrent Resolution](https://en.wikipedia.org/wiki/Concurrent_resolution)
- [House passes FAA reauthorization bill](https://www.cnn.com/2018/04/27/politics/faa-reauthorization-transportation-house-congress/index.html)
- [FAA Reauthorization Act of 2018 Summary](https://www.govtrack.us/congress/bills/115/hr4/summary)


